Chronic imaging of cortical oxygen tension and blood flow after targeted vascular occlusion

### 2018-04-13 article.tex
Better focus and more details on wavelength dependence

In this paper we present an update to the system by Ponticorvo and Dunn \cite{Ponticorvo:2010uv} that utilizes a more robust porphyrin probe \cite{Esipova:2011hi} and offers higher spatiotemporal resolutions for both LSCI and phosphorescence lifetime imaging. The system is capable of illuminating either of the phosphorescent probe's excitation maxima, allowing us to examine the relationship between wavelength and \pO. We demonstrate the ability to detect static variations in \pO\ between different types of vasculature and the dynamic monitoring of blood flow and \pO\ during DMD-targeted photothrombotic stroke. We also demonstrate chronic imaging by tracking the response to the ischemic event over several days. This system allows for acute and chronic imaging of relative blood flow and oxygen tension and has broad applications for both basic neuroscience and neuropathophysiology.

@@

A calibration curve based on Stern-Volmer kinetics \cite{Vanderkooi:1986hs,Wilson:2003ek} was used to convert the measured lifetime ($\tau$) to the absolute \pO. The calibration of Oxyphor PtG4 under physiological conditions is shown in Fig.~\ref{fig:oxyphor_ptg4}b. The unquenched lifetime is 47 $\mu$s in an oxygen-free environment. Fig.~\ref{fig:oxyphor_ptg4}c depicts phosphorescent decay curves and their corresponding \pO\ values within anoxic and normoxic cuvette environments with 10 $\mu$M Oxyphor PtG4. Anoxia was established using the enzymatic reaction between glucose and glucose oxidase to scavenge oxygen from a sealed cuvette \cite{Lo:1997he}. Lifetime measurements and therefore \pO\ values did not vary with excitation wavelength.

% Figure 2 - Oxyphor PtG4
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure2.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:oxyphor_ptg4}
        (a) Excitation and emission spectra for Oxyphor PtG4. Dashed vertical lines indicate excitation lasers at 445 nm and 637 nm. (b) Calibration curve relating \pO\ to the measured phosphorescence lifetime ($\tau$) under physiological conditions (37 $^\circ$C, pH 7.2). For $\tau < 16$ $\mu$s, Stern-Volmer kinetics were assumed with $k_q = 291.014$ mmHg$^{-1}$ s$^{-1}$ and $\tau_0 = 47$ $\mu$s. (c) Averaged phosphorescent decay curves ($n = 200$) in anoxic and normoxic cuvette environments with fitted lifetimes and their corresponding \pO\ values.
    }
\end{figure}

@@

\subsection{Static Oxygen Tension}
Static oxygen tension measurements in the neurovasculature of the mouse cortex are shown in Fig. 3. Five different regions including two arterioles, two veins, and an area of unresolvable vasculature (parenchyma) were targeted for selective illumination using both the 445 nm and 637 nm excitation lasers (Fig.~\ref{fig:static_oxygen}a). The calculated \pO\ within each region aligns well with physiological expectations as both arterioles have higher \pO\ than the venous or parenchymal areas (Fig.~\ref{fig:static_oxygen}b). The effects of wavelength can be seen as 445 nm excitation resulted in a broader range of oxygen tension values (48 - 83 mmHg) compared to 637 nm excitation (75 - 82 mmHg). Despite differences in absolute value, similar trends can be seen between each of the targeted regions with both excitation wavelengths.

>>>>

In this paper we present an update to the system by Ponticorvo and Dunn \cite{Ponticorvo:2010uv} that utilizes a more robust porphyrin probe \cite{Esipova:2011hi} and offers higher spatiotemporal resolutions for both LSCI and phosphorescence lifetime imaging. Using both of the phosphorescent probe's excitation maxima, we highlight wavelength-dependent differences in measured decay lifetimes. We demonstrate the ability to detect static variations in \pO\ between different types of vasculature and the dynamic monitoring of blood flow and \pO\ during DMD-targeted photothrombotic stroke. We also demonstrate chronic imaging by tracking the response to the ischemic event over several days. This system allows for acute and chronic imaging of relative blood flow and oxygen tension and has broad applications for both basic neuroscience and neuropathophysiology.

@@

A calibration curve based on Stern-Volmer kinetics \cite{Vanderkooi:1986hs,Wilson:2003ek} was used to convert the measured lifetime ($\tau$) to the absolute \pO. The calibration of Oxyphor PtG4 under physiological conditions is shown in Fig.~\ref{fig:oxyphor_ptg4}b. The unquenched lifetime is 47 $\mu$s in an oxygen-free environment. Fig.~\ref{fig:oxyphor_ptg4}c depicts phosphorescent decay curves and their corresponding \pO\ values within anoxic and normoxic cuvette environments with 10 $\mu$M Oxyphor PtG4. Anoxia was established using the enzymatic reaction between glucose and glucose oxidase to scavenge oxygen from a sealed cuvette \cite{Lo:1997he}. Lifetime measurements in cuvette samples did not vary with excitation wavelength (Fig.~\ref{fig:oxyphor_ptg4}d).

% Figure 2 - Oxyphor PtG4
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure2.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:oxyphor_ptg4}
        (a) Excitation and emission spectra for Oxyphor PtG4. Dashed vertical lines indicate excitation lasers at 445 nm and 637 nm. (b) Calibration curve relating \pO\ to the measured phosphorescence lifetime ($\tau$) under physiological conditions (37 $^\circ$C, pH 7.2). For $\tau < 16$ $\mu$s, Stern-Volmer kinetics were assumed with $k_q = 291.014$ mmHg$^{-1}$ s$^{-1}$ and $\tau_0 = 47$ $\mu$s. (c) Averaged phosphorescent decay curves ($n = 200$) in anoxic and normoxic cuvette environments with fitted lifetimes and their corresponding \pO\ values. (d) \pO\ measurements did not vary with excitation wavelength.
    }
\end{figure}

@@

\subsection{Excitation Wavelength Dependence of Measured Oxygen Tension}
Static oxygen tension measurements in the neurovasculature of the mouse cortex are shown in Fig. 3. Five different regions including two arterioles, two veins, and an area of unresolvable vasculature (parenchyma) were targeted for selective illumination using both the 445 nm and 637 nm excitation lasers (Fig.~\ref{fig:static_oxygen}a). The calculated \pO\ within each region aligns well with physiological expectations as both arterioles have higher \pO\ than the venous or parenchymal areas (Fig.~\ref{fig:static_oxygen}b). The effects of wavelength can be seen as 445 nm excitation resulted in a broader range of oxygen tension values (48 - 83 mmHg) compared to 637 nm excitation (75 - 82 mmHg). Despite differences in absolute value, similar trends can be seen between each of the targeted regions with both excitation wavelengths. As shown previously in Fig.~\ref{fig:oxyphor_ptg4}d, no differences in \pO\ were observed between the two wavelengths in cuvette samples.
